\begin{thebibliography}{99}
\bibitem{he1} E. D. Pisano $et$ $al$, ``Contrast limited adaptive histogram equalization image processing to improve the detection of simulated speculations in dense mammograms,'' J. Digit. Image, vol. 11, no. 4, pp. 193-200, 1998.
\bibitem{he2} H, Cheng and X. Shi, ``A simple and effective histogram equalization approach to image enhancement,'' Digital Signal Processing, vol. 14, no. 2, pp. 158-170, 2004.
\bibitem{he3} S.-C. Huang, F.-C. Cheng, and Y.-S. Chiu, ``Efficient contrast enhancement using adaptive gama correction with weighting distribution,'' IEEE Trans. Image Process., vol. 20, no. 5, pp. 1262-1272, 2011.
\bibitem{haze1} L. Li, R. Wang, W. Wamg, and W. Gao, ``A low-light image enhancement method for both denoising and contrast enlarging,'' in Proc. IEEE Int. Conf. Image Process., pp. 3730-3734, 2015.
\bibitem{haze2} X.Zhang, P.Shen, L. Luo, L. Zhang, and J. Song, ``Enhancement and noise reduction of very low light level images,'' in Proc. 21st Int. Conf. Pattern Recognit. (ICPR), pp. 2034-2037, 2012. 
\bibitem{ssr} D. J. Jobson, Z.-U. Rahman, and G. A. Woodell, ``Properties and performance of a center/surround retinex,'' IEEE Trans. Image Process., vol. 6, no. 3, pp. 451-462, 1997.
\bibitem{msr} D. J. Jobson, Z.-U. Rahman, and G. A. Woodell, ``A multiscale retinex for briding the gap between color images and the human observation of scenes,'' IEEE Trans. Image Process, vol. 6, no. 7, pp. 965-976, 1997.
\bibitem{srie}X. Fu, Y. Liao, D. Zeng, Y. Huang, X. Zhang, and X. Ding, ``A probabilistic method for image enhancement with simultaneous illumination and reflectance estimation,'' IEEE Trans. Image Process., vol. 24, no. 12, pp. 4965-4977, 2015.
\bibitem{wvm}X. Fu, D. Zeng, Y. Huang, X. Zhang and X. Ding, ``A weighted variational model for simultaneous reflectance and illumination estimation, '' IEEE Conf. Computer Vis. Pattern Recognit., pp. 2782-2790, 2016.
\bibitem{lime} X. Guo, Y. Li, and H. Ling, ``LIME: Low-light image enhancement via illumination map estimation,'' IEEE Trans. Image Process., vol. 26, no. 2, pp. 982-993, 2017. 
\bibitem{jiep} B. Cai, X. Xu, K. Guo, K. Jia, B. Hu, and D. Tao, ``A joint intrinsic-extrinsic prior model for retinex,'' In Proc., IEEE Conf. Computer Vis., Pattern Recognit., pp. 4000-4009, 2017.
\bibitem{rrm} M. Li, J. Liu, W. Yang, X. Sun, and Z. Guo, ``Structure-revealing low-light image enhancement via robust Retinex model, '' IEEE Trans. Image Process., vol. 27, no. 6, pp. 2828-2841, 2018.
\bibitem{retinex} E. H. Land and J. J. McCann, ``Lightness and retinex theory,'' J. Opt. Soc. Amer., vol. 61, no. 1, pp. 1-11, 1971.
\bibitem{guided} K. He, J. Sun, and X. Tand, ``Guided image filtering,'' Proc. European Conf. on Computer Vis., pp. 1-14, 2010.
\bibitem{l2-lp} C. Fu, L. Duan, and C. Xiao, ``A hybrid L2-Lp variational model for single low-light image enhancement with bright channel prior,'' IEEE Int. Conf. on Image Process. (ICIP), 2019.
\bibitem{arpr} N. Bonneel, B. Kovacs, S. Paris, and K. Bala, ``Intrinsic decompositions for image editing,'' Computer Graphics Forum, vol.36, no. 2, 2017.
\bibitem{block} P. Tseng, ``Convergence of a block coordinate descent method for nondifferentiable minimization,'' Journal of Optimization Theory and Applications, vol. 109, no. 3, pp. 475-494, 2001.
\bibitem{iterate} E. J. Candes, M. B. Wakin, and S. P. Boyd, ``Enhancing sparsity by reweighted $l_{1}$ minimization,'' Journal of Fourier Analysis and Applications, vol. 14, no. 5-6, pp. 877-905, 2008. 
\bibitem{l0-sparse} L. Xu, S.Zheng, and J. Jia, ``Unnatural l0 sparse representation for natural image debluring,'' IEEE Conf. Computer Vis. Pattern Recognit., pp. 1107-1114, 2013.
\bibitem{bright} X. Fu, D. Zheng, Y. Huang, X. Ding, and X-P. Zhang, ``A variational framework for single low light image enhancement using bright channel prior, '' in Proc. IEEE Global Conf. on Signal and Inform. Process., pp. 1085-1088, 2013.
\bibitem{activation} S. Park, S. Yu, B. Moon, S. Ko, and J. Paik, ``Low-light image enhancement using variational optimization-based retinex model,'' IEEE Trans. on Cons. Elec., vol. 63, no. 2, pp. 178-184, 2017.
\bibitem{loe} S. Wang, J. Zheng, H.-M. Hu, and B. Li, ``Naturalness preserved enhancement algorithm for non-uniform illumination images,'' IEEE Trans. Image Process., vol. 22, no. 9, pp. 3538-3578, 2013.
\bibitem{arism} K. Gu, G. Zhai, W. Lin, X. Yang, and W. Zhang, ``No reference image sharpness assessment in autoregressive parameter space,'' IEEE Trans. on Image Process., vol. 24, no. 10, pp. 3218-3231, 2015.
\end{thebibliography}